
```{r, include=F, echo=F, message=F, warning=F}
library(stringr)
library(rvest)
library(dplyr)

nycook<-read_html("http://cooking.nytimes.com/68861692-nyt-cooking/3891782-our-50-most-popular-recipes-of-2016")
url<-"http://cooking.nytimes.com/68861692-nyt-cooking/3891782-our-50-most-popular-recipes-of-2016"
cook<-readLines(url)##read webpage
##pull url for weblinks
web_url<-'data-url=\"'
recipe_pages<-grep(web_url, cook[243:length(cook)], value=TRUE)##pull addys
recipe_id<-gsub(web_url, "", recipe_pages)%>% ##clean up link ids
  gsub(pattern='"',replacement= "")%>%
  str_trim(side="both")
recipe_id##looks good

####################################
recipe_ingredients=NULL ##empty df
##loop to pull ingredients from all recipes in list from nytimes
for (i in recipe_id){
  ##extract keys for each recipe and extract web text
  site_pre<-'http://cooking.nytimes.com'
  site_post<-'?action=click&module=Collection+Page+Recipe+Card&region=Our+50+Most+Popular+Recipes+of+2016&pgType=collection&rank=1'
  recipe_site<-paste0(site_pre, i, site_post)
  recipe<-readLines(recipe_site)
  #extract ingredients
  ing_pattern<-'<span class=\"ingredient-name\">'
  ing_list<-grep(ing_pattern, recipe[300:length(recipe)], value=TRUE)
  #clean ingredient
  ingredients<-gsub(ing_pattern, "", ing_list)%>%
    tolower()%>%
    gsub(pattern='</span>', replacement="")%>%
    gsub(pattern='<span>', replacement="")%>%
    gsub(pattern="\\,.*", replacement="")%>%
    gsub(pattern='[0-9]+', replacement='')%>%
    str_replace_all(pattern="[^[:alnum:]]", replacement=" ")
  rec_name<-gsub(i, pattern="^.*?\\-", replacement="") ##convert url to recipe name
  ##remove extra wordage
  measures<-c("teaspoon","two","ct","tablespoon","more","teaspoons","handful","ears ","stems of","sleeve","large","diced", "sprig","to taste","tablespoons"," can ","cup","pounds","pound","cups","stick","sticks","pint","quart","pinch","gallon","ounce","grams","ounces","gallons","quarts","pints","kg","mg","milliliters")
  adjectives<-c("dry","young","good quality brine cured ","basic"," not quick cooking","hungarian ","italian","rib","like soom","liquid","seed","smooth","thick","cooked","grappa","crushed","use a food processor if you have one","from ","torn","stems","to ","coarse","at room temperature","heaping","optional","white","fleshed","chopped","loosely","small","ripe","yellow","boneless","squeezed","stalks","rich","prepared","about"," of "," or","mixed","slivered"," day "," old ","fine","rolled","raw ","wild"," and ","unsalted","ripe","bunch","firm","size","plus","head","neutral","cleaned","extra","very","sifted","branches","kosher","yellow","juice","zest","paste","clove","cloves","tender","leaves","large","fresh","sprigs","skinless","medium","small","diced","chopped","thick","slices","sliced","minced","packed","loosely","flaky","handful","crushed","roughly","pitted","finely","low sodium","whole","cold","hot","warm","toasted","roasted","grated","shredded","peeled","skinned","freshly","unsweetened","canned","dried","ground")
  ing_o <- as.character(sapply(ingredients, function(x) 
    gsub(paste(measures, collapse = '|'), '', x)))
  ing_only <- as.character(sapply(ing_o, function(x) 
    gsub(paste(adjectives, collapse = '|'), '', x)))
  ing_only<-gsub(ing_only, pattern="s ", replacement="")
  ing_only<-gsub(ing_only, pattern="  ", replacement=" ")
  ing_only<-gsub(ing_only, pattern="  ", replacement=" ")
  ing_only<-ing_only%>%str_trim(side="both")#clean whitespace
  ingreds<-data.frame(recipe = rep(rec_name,length(ing_only)), ingredient = ing_only)
  ingreds<-ingreds[!grepl("href", ingreds$ingredient),]
  recipe_ingredients=rbind(recipe_ingredients,ingreds)#return df
}

ez<-recipe_ingredients
ez$ingredient<-as.character(ez$ingredient)
ez$ingredienty<-as.character(ifelse(grepl("olive oil", ez$ingredient), 'oliveoil',
                                    ifelse(grepl("salt black pepper", ez$ingredient), 'salt',
                                           ifelse(grepl("black pepper", ez$ingredient), 'blackpepper',
                                           ifelse(grepl("saltpepper", ez$ingredient), 'blackpepper',
                                                  ifelse(grepl("chicken", ez$ingredient), 'chicken',
                                                         ifelse(grepl("mushroom", ez$ingredient), 'mushroom',
                                                                ifelse(grepl("sugar", ez$ingredient), 'sugar',
                                                                       ifelse(grepl("toma", ez$ingredient), 'tomato',
                                                                              ifelse(grepl("bone in", ez$ingredient), "chicken",
                                                                                     ifelse(grepl("bacon", ez$ingredient), 'bacon',
                                    ifelse(grepl("lemon", ez$ingredient), 'lemon', 
                                           ifelse(grepl("bread", ez$ingredient), 'bread',
                                                  ifelse(grepl("butter", ez$ingredient), 'butter',
                                                    ifelse(grepl("butter", ez$ingredient), 'butter',
                                                           ifelse(grepl("stock", ez$ingredient), 'stock',
                                                                  ifelse(grepl("turmeric", ez$ingredient), 'turmeric',
                                                                         ifelse(grepl("thyme", ez$ingredient), 'thyme',
                                                                                (ifelse(grepl("tamarind", ez$ingredient), 'tamarind',
         ifelse(grepl("shrimp", ez$ingredient), 'shrimp',
                ifelse(grepl("saffron", ez$ingredient), 'saffron',
                       ifelse(grepl("red chile flakes", ez$ingredient), 'red pepper flakes',
                              ifelse(grepl("yogurt", ez$ingredient), 'yogurt',
                                     ifelse(grepl("carrot", ez$ingredient), 'carrot',
                                            ifelse(grepl("black pepper", ez$ingredient), 'black pepper',
                                                   ifelse(grepl("beef", ez$ingredient), 'beef',
                                                          ifelse(grepl("mustard", ez$ingredient), 'mustard', 
                                                                 ifelse(grepl("anchov", ez$ingredient), 'anchovies',
                                                                        ifelse(grepl("potato", ez$ingredient), 'potato',
                                                                               ifelse(grepl("mint", ez$ingredient), 'mint',
                                                                                      ifelse(grepl("chocolate", ez$ingredient), 'chocolate',
                                                                                             ifelse(grepl("cocoa", ez$ingredient), 'chocolate',
                                                                                                    ifelse(grepl("ecchiette", ez$ingredient), 'ecchiette',
                                                                                                           ifelse(grepl("egano", ez$ingredient), 'oregano',
                                                                                                                  ifelse(grepl("cardamom", ez$ingredient), 'cardamom',
                                                                                                                         ifelse(grepl("gruyère", ez$ingredient), 'gruyère',
                                                                                                                                ifelse(grepl("jalapeño", ez$ingredient), 'jalapeño',
                                                                                                                                       ifelse(grepl("parmigiano", ez$ingredient), 'parmesan',
                                                                                                                                              ifelse(grepl("kale", ez$ingredient), 'kale',
                                                                                                                                                     ifelse(grepl("lime", ez$ingredient), 'lime',
                                                                                                                                                            ifelse(grepl("onion", ez$ingredient), 'onion',
                                                                                                                                                                   ifelse(grepl("tahini", ez$ingredient), 'tahini',
                                                                                                                                                                          ifelse(grepl("nutmeg", ez$ingredient), 'nutmeg',
                                                                                                                                                                                 ifelse(grepl("paprika", ez$ingredient), 'paprika',
                                                                                                                                                                                        ifelse(grepl("parmesan", ez$ingredient), 'parmesan',
                                                                                                                                                                                               ifelse(grepl("feta", ez$ingredient), 'feta',
                                                                                                                                                                                                      ifelse(grepl("flour", ez$ingredient), 'flour',
                                                                                                                         
                                                                 ez$ingredient))))))))))))))))))))))))))))))))))))))))))))))))

##ingredient counts
df<-ez%>%
  group_by(ingredienty)%>%
  summarize(recipes_in = length(recipe))
df_short<-filter(df, df$recipes_in>=3)
ings<-df_short$ingredienty
##make adjacency matrix
library(reshape2)
fd<-ez[,c("recipe","ingredienty")]
fd.melt<-melt(fd, id.vars=c("recipe"),na.rm=FALSE)
fd.melt<-filter(fd.melt, value %in% ings)
trec_cast<-dcast(fd.melt, recipe~value,fill=0, drop=FALSE)

rec_wide<-trec_cast%>%select(-salt, -butter, -garlic, -oil, -blackpepper, -oliveoil, -Var.2)

###wide df- recipe x ingredients
recs<-rec_wide[,-1]
rownames(recs)<-rec_wide$recipe
rec<-as.matrix(recs)
###network data
##adjacency matrix
#by ingredients

ing_adj<-crossprod(rec)


##recipes similar to one another
rec_adj<-crossprod(t(rec))##recipes with simialr ingredients

##make network visualization
library(igraph)
library(network)
library(sna)
library(ndtv)
library(visNetwork)

net3<-graph_from_adjacency_matrix(ing_adj, diag=FALSE, mode="undirected", weighted=TRUE)
net <- simplify(net3, remove.multiple = T, remove.loops = T)
E(net)$width<- 1+E(net)$weight/5
```
```{r, fig.width=11, fig.height=11, echo=F}

plot(net, vertex.label=V(net3)$recipe, edge.color="lightseagreen",
     vertex.color="white", vertex.frame.color="#ffffff", vertex.label.color="black",
     vertex.label.cex=1, edge.color="gray85",edge.curved=.1,vertex.shape="none",
     vertex.label.font=2,
     layout=layout_with_mds, edge.width=E(net)$width)
```

This visualization is based on the 50 most popular recipes of 2016 by NY Times Cooking. This is a dataset I created by scraping the webpage of each recipe (http://cooking.nytimes.com/68861692-nyt-cooking/3891782-our-50-most-popular-recipes-of-2016) for its’ ingredient list. Then I cleaned the dataset to obtain common naming for each ingredient and removing adjectives and measurements. I removed the most common ingredients (olive oil, butter, salt, pepper), then I created an adjacency matrix for each ingredient where the edges between ingredients are indicative of the number of recipes they are in together. The width of the edges reflects the number of recipes each ingredient pair is found in together and nodes are spaced relative to one another based on how similar they are in the recipes they are found in.   

